A comparison of design-based and model-based approaches for finite population spatial data -- Supporting information.

### 2022-06-11 inst/manuscript/supporting.Rmd
minor updates pre zenodo

Next we present tables summarizing mean bias, RMSE, and interval coverage for all 36 simulation scenarios.
```{r}
make_sim_table <- function(table_value) {
  # browser()
  sim_table <- read_csv(here("inst", "output", "simulation_summary", paste0("allsims", table_value, ".csv")))
  sim_table <- sim_table %>%
    mutate(psill_ratio = paste0(100 * psill_ratio, "%")) %>%
    dplyr::select(Approach = approach,
                  Layout = gridded,
                  Response = resptype,
                  `DRE%` = psill_ratio,
                  n = n,
                  MB = mpbias,
                  RMSE = rmspe,
                  Coverage = coverage
                  ) %>%
    mutate(
     Approach = case_when(
       Approach == "Design GRTS" ~ "GRTS-DB",
       Approach == "Design IRS" ~ "SRS-DB",
       Approach == "Model GRTS" ~ "GRTS-MB",
       Approach == "Model IRS" ~ "SRS-MB"
     ),
     Layout = case_when(
        Layout ~ "Gridded",
        !Layout ~ "Random"
      ),
     Response = case_when(
       Response == "normal" ~ "Normal",
       Response == "lognormal" ~ "Skewed"
     ),
     across(c(`DRE%`, n), as.character)
    )
sim_table <- sim_table[c(2, 4, 1, 3), ]
sim_table_out <- xtable(
  sim_table,
  digits = 4,
  caption = paste0("Sampling-inference combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DRE\\%), sample size (n), mean bias (MB), root-mean-squared error (RMSE), and 95\\% interval coverage (Coverage) in simulation scenario ", table_value, "."),
   type = "latex",
  latex.environments = "center",
  align = c("llllrrrrr")
)
print(sim_table_out, include.rownames = FALSE, comment = FALSE, scalebox = "0.8")
}
```

@@

Next we present tables summarizing mean bias, RMSE, and interval coverage for all six data scenarios.
```{r}
make_data_table <- function(table_value) {
  # browser()
  data_table <- read_csv(here("inst", "output", "data_summary", paste0("datasims", table_value, ".csv")))
  data_table <- data_table %>%
    dplyr::select(Approach = approach,
                  Response = var,
                  n = n,
                  MB = mpbias,
                  RMSE = rmspe,
                  Coverage = coverage
                  ) %>%
    mutate(
     Approach = case_when(
       Approach == "Design GRTS" ~ "GRTS-DB",
       Approach == "Design IRS" ~ "SRS-DB",
       Approach == "Model GRTS" ~ "GRTS-MB",
       Approach == "Model IRS" ~ "SRS-MB"
     ),
     Response = case_when(
       Response == "MMI_ZOOP_NLA6" ~ "ZMMI",
       Response == "TOTALHG_RESULT" ~ "Hg ppb"
     ),
     across(c(n), as.character)
    )
data_table <- data_table[c(2, 4, 1, 3), ]
data_table_out <- xtable(
  data_table,
  digits = 4,
  caption = paste0("Sampling-inference combination (Approach), response type (Response), sample size (n), mean bias (MB), root-mean-squared error (RMSE), and 95\\% interval coverage (Coverage) in a data application scenario ", table_value, "."),
   type = "latex",
  latex.environments = "center",
  align = c("lllrrrr")
)
print(data_table_out, include.rownames = FALSE, comment = FALSE, scalebox = "0.8")
}
```

>>>>

Next we present tables summarizing mean bias, RMSE, and interval coverage for all 36 simulation scenarios.
```{r}
make_sim_table <- function(table_value) {
  # browser()
  sim_table <- read_csv(here("inst", "output", "simulation_summary", paste0("allsims", table_value, ".csv")))
  sim_table <- sim_table %>%
    mutate(psill_ratio = paste0(100 * psill_ratio, "%")) %>%
    dplyr::select(Approach = approach,
                  Layout = gridded,
                  Response = resptype,
                  `DRE%` = psill_ratio,
                  n = n,
                  MBias = mpbias,
                  RMSE = rmspe,
                  Coverage = coverage
                  ) %>%
    mutate(
     Approach = case_when(
       Approach == "Design GRTS" ~ "GRTS-DB",
       Approach == "Design IRS" ~ "SRS-DB",
       Approach == "Model GRTS" ~ "GRTS-MB",
       Approach == "Model IRS" ~ "SRS-MB"
     ),
     Layout = case_when(
        Layout ~ "Gridded",
        !Layout ~ "Random"
      ),
     Response = case_when(
       Response == "normal" ~ "Normal",
       Response == "lognormal" ~ "Skewed"
     ),
     across(c(`DRE%`, n), as.character)
    )
sim_table <- sim_table[c(2, 4, 1, 3), ]
sim_table_out <- xtable(
  sim_table,
  digits = 4,
  caption = paste0("Sampling-inference combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DRE\\%), sample size (n), mean bias (MBias), root-mean-squared error (RMSE), and 95\\% interval coverage (Coverage) in simulation scenario ", table_value, "."),
   type = "latex",
  latex.environments = "center",
  align = c("llllrrrrr")
)
print(sim_table_out, include.rownames = FALSE, comment = FALSE, scalebox = "0.8")
}
```

@@

Next we present tables summarizing mean bias, RMSE, and interval coverage for all six data scenarios.
```{r}
make_data_table <- function(table_value) {
  # browser()
  data_table <- read_csv(here("inst", "output", "data_summary", paste0("datasims", table_value, ".csv")))
  data_table <- data_table %>%
    dplyr::select(Approach = approach,
                  Response = var,
                  n = n,
                  MBias = mpbias,
                  RMSE = rmspe,
                  Coverage = coverage
                  ) %>%
    mutate(
     Approach = case_when(
       Approach == "Design GRTS" ~ "GRTS-DB",
       Approach == "Design IRS" ~ "SRS-DB",
       Approach == "Model GRTS" ~ "GRTS-MB",
       Approach == "Model IRS" ~ "SRS-MB"
     ),
     Response = case_when(
       Response == "MMI_ZOOP_NLA6" ~ "ZMMI",
       Response == "TOTALHG_RESULT" ~ "Hg ppb"
     ),
     across(c(n), as.character)
    )
data_table <- data_table[c(2, 4, 1, 3), ]
data_table_out <- xtable(
  data_table,
  digits = 4,
  caption = paste0("Sampling-inference combination (Approach), response type (Response), sample size (n), mean bias (MBias), root-mean-squared error (RMSE), and 95\\% interval coverage (Coverage) in a data application scenario ", table_value, "."),
   type = "latex",
  latex.environments = "center",
  align = c("lllrrrr")
)
print(data_table_out, include.rownames = FALSE, comment = FALSE, scalebox = "0.8")
}
```
